### 2025-05-20 conteudo/results/students.tex
add some work

% As presented in chapter \ref{cha:methods}, we propose to students to mitigate duplications
% found by the ArKanjo tool and send patches to the linux subsystems maintainers, while
% documenting their experiences and learning through the process. 
% 
% For the students that worked
% in the IIO subsytems, we gave them duplicated function pairs found by the tool and their 
% responsability was to think of how to mitigate the duplication and sent the patch to the 
% maintainers. The student that worked in the AMD Display driver have the additional work
% to use the tool to find the duplications.
% 
% Appendix (CREATE APPENDIX AND ADD HERE X) has references
% to the artifacts discussed in this section, including the duplication function pairs that students 
% mitigate, the students's reports, the patch students sent to the linux kernel, and the 
% answers of the questionary asked to the student that worked in the AMD Display driver and the 
% teaching assistant that used the tool to find duplications in the IIO.
% 
% \input{conteudo/results/table_students}
% 
% Table (CREATE TABLE AND ADD HERE X) summarizes the mitigation approachs of the students in terms 
% of lines changed and refactor methods used. BLABLABLA
% 
% 
% \subsection{Questionary Answers}
% 
% BLABLABLA

>>>>

As presented in chapter \ref{cha:method}, we propose to students to mitigate duplications
found by the ArKanjo tool and send patches to the linux subsystems maintainers, while
documenting their experiences and learning through the process.

For the students that worked
in the IIO subsytems, we gave them duplicated function pairs found by the tool and their 
responsability was to think of how to mitigate the duplication and sent the patch to the 
maintainers. The student that worked in the AMD Display driver have the additional work
to use the tool to find the duplications.

Appendix (CREATE APPENDIX AND ADD HERE X) has references
to the artifacts discussed in this section, including the duplication function pairs that students 
mitigate, the students's reports, the patch students sent to the linux kernel, and the 
answers of the questionary asked to the student that worked in the AMD Display driver and the 
teaching assistant that used the tool to find duplications in the IIO.

\input{conteudo/results/table_students}

Table (CREATE TABLE AND ADD HERE X) summarizes the mitigation approachs of the students in terms 
of lines changed and refactor methods used. BLABLABLA

\subsection{Questionary Answers}

BLABLABLA
